\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\LARGE Joshua Nichols} \\ \vspace{3pt}
    \small \href{mailto:joshuani@cmu.edu}{\faEnvelope~joshuani@cmu.edu} $|$ 
    \href{https://github.com/joshuaan}{\faGithubSquare~joshuaan} $|$
    \href{https://linkedin.com/in/joshuaanichols}{\faLinkedinSquare~joshuaanichols}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Bachelor of Science, Electrical and Computer Engineering, 3.55/4.0 GPA}{Aug 2023 -- May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant coursework:} Principles of Real Analysis I, Algebraic Structures, Probability Theory, Great Theoretical Ideas in Computer Science, Computer Systems, Principles of Functional Programming.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Teaching Assistant}{Aug 2024 - Present}
      \resumeItemListStart
        \resumeItem{Taught weekly recitations and labs to undergraduate students for Carnegie Mellon's C programming + Data Structures and Algorithms course.}
        \resumeItem{Graded homework, programming assignments, and exams for correctness and style in C.}
        \resumeItem{Collaborated with group of 40+ staff members to run course of over 400 students.}
      \resumeItemListEnd

    \resumeSubheading
      {NASA Langley Research Center}{Hampton, VA}
      {Computer Science Research Intern}{Jun 2024 - Aug 2024}
      \resumeItemListStart
        \resumeItem{Implemented new data association methods for sensor fusion in OCaml and PVS, a NASA developed mathematical theorem prover, with graph theory algorithms and Kalman filters.}
        \resumeItem{Developed work on proving robustness properties about Kalman filters and data association methods using real analysis in the PVS theorem prover.}
        \resumeItem{Proved over 100 fundamental linear algebra theorems in NASA core library with the PVS theorem prover.} 
      \resumeItemListEnd

    \resumeSubheading
      {Robotic Exploration Lab - Carnegie Mellon University}{Pittsburgh, PA}
      {Research Assistant}{Jan 2024 - Apr 2024}
      \resumeItemListStart
        \resumeItem{Rewrote numerical optimization solver in C++ to improve maintainability and development capabilities of codebase}
        \resumeItem{Improved benchmark time of optimization solver by 20\% with low-level C++ techniques and algorithmic improvements.}
      \resumeItemListEnd
    
    \resumeSubheading
      {NASA Langley Research Center}{Hampton, VA}
      {Software Engineer Intern}{Jun 2023 - Aug 2023}
      \resumeItemListStart
        \resumeItem{Implemented reinforcement learning methods with PyTorch for optimal control of robotic systems.}
        \resumeItem{Improved size of numerical flight simulations by over 100x according to benchmarks through GPU parallelization and algorithmic improvements.}
        \resumeItem{Created visualization tools for robotic system and flight simulations in Unity with C\#.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Numerical Optimization Solver - Sleipnir}{}
      {\href{https://github.com/SleipnirGroup/Sleipnir}{https://github.com/SleipnirGroup/Sleipnir}}{}
      \resumeItemListStart
        \resumeItem{Founded open-source research project and numerical optimization solver, Sleipnir, written in C++.}
        \resumeItem{Benchmarks show Sleipnir is over 2x faster than state-of-the-art research and industry solvers as a result of novel differentiable programming developments.}
        \resumeItem{Sleipnir is used in production by over 5,000 users in FIRST Robotics Competition as part of motion planning app.}
        \resumeItem{300 active users and contributors in development Discord server.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Awards}
  \resumeItemListStart
    \resumeItem{NASA Robotics Alliance Project Medal of Excellence}
  \resumeItemListEnd


\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Programming languages:} C, C++, OCaml, Python, MATLAB, Java, Javascript, HTML/CSS}
  \resumeItemListEnd


%-------------------------------------------
\end{document}